---
title: "Untitled"
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prerequisites

Install the following packages

- dplyr
- ggplot2
- rsample
- modeldata
- caret
- h2o
- AmesHousing


## Initiate the H2O environment

```{r}
# Helper packages
library(dplyr)     # for data manipulation
library(ggplot2)   # for awesome graphics

# Modeling process packages
library(rsample)   # for resampling procedures
library(caret)     # for resampling and model training
library(h2o)       # for resampling and model training

# h2o set-up 
h2o.no_progress()  # turn off h2o progress bars
h2o.init()         # launch h2o
```


What if you got the following error:

```
<simpleError in system2(command, "-version", stdout = TRUE, stderr = TRUE): '-version' not found>
Error in value[[3L]](cond) : 
  You have a 32-bit version of Java. H2O works best with 64-bit Java.
Please download the latest Java SE JDK from the following URL:
https://www.oracle.com/technetwork/java/javase/downloads/index.html
```

This error suggests that h2o initiation could not find the needed Java,
which can be caused by:

- no java was installed on the system
- 32-bit, instead of 64-bit Java was installed
- the environment variable *JAVA_HOME* was not set

Therefore, one needs to install the 64-bit Java or JDK, and then set environment
variable *JAVA_HOME* to the installation folder, such as 
*c:/Program Files/Java/jdk-23*, and then restart R and reinstall the package
*h2o*, and this should solve the problem. For more on the package, check this
link https://docs.h2o.ai/h2o/latest-stable/h2o-docs/faq/r.html.


## Load data

```{r}
# Ames housing data
ames <- AmesHousing::make_ames()
ames.h2o <- as.h2o(ames)

# Job attrition data
churn <- modeldata::attrition %>% 
  mutate_if(is.ordered, .funs = factor, ordered = FALSE)
churn.h2o <- as.h2o(churn)
```



